TITLE

### 2021-02-21 outputs/paper/paper.Rmd
typo

In addition to survey data collected by Petit Poll, this report relies on publicly available federal census data [@census_2016] and data from provincial public health departments[@inspection].

>>>>

In addition to survey data collected by Petit Poll, this report relies on publicly available federal census data [@census_2016] and data from provincial public health departments [@inspection].
